\newpage
\TOCadd{Acknowledgements}

\begin{center}
ACKNOWLEDGEMENTS
\end{center}
%
\noindent

Unprecedented. That word has been used more than any other to describe the circumstances surrounding the last two years. The majority of my time at the University of Victoria has been overshadowed by the COVID-19 pandemic. Undertaking a major research project through such ``unprecedented" times has required an unparalleled amout of support. The list of people who have helped me through this thesis is far too long to include in a single page, but I would like to give thanks to a select few who have had an especially lage impact:
\begin{description}
\item[Healthcare workers,]
  in Canada and worldwide. Your tireless work and boundless compassion have been an inspiration, and we wouldn't be here without you.
\item[Dr. Justin Albert,]
  for seamlessly navigating the challenges of supervising me and my scatterbrain through zoom calls and emails.
\item[Danika MacDonell,]
  for welcoming me into the analysis team, and for your patience and kindness showing me the ins and outs of being an ATLAS analyst.
\item[The Mono-s analysis team,]
  Philipp, Dr. Hamano, and Dr. Kowalewski for your help and feedback throughout this project.
\item[My family,]
  Mom, Dad, Emily, and Claire, for always pushing me to succeed, but showing me the same love and encouragement no matter what. You are the world's very best support network.
\item[My partner,]
	Jaedyn, for always being by my side. From you, that means the world.
\end{description}
%
\begin{flushright}
\textit{La  lutte  elle-même  vers  les  sommets suffit à remplir un cœur d'homme. Il faut imaginer Sisyphe heureux.}
\\
Albert Camus \\
\end{flushright}
